Structuring College Access

### 2025-06-27 index.qmd
update rq2 graphs + tables

    return(
      kbl(
        table_df %>%
          mutate(
            across(all, \(x) format(round(x, 0), big.mark = ',')),
            across(known, ~ if_else(table == 'col_pct_table' & eps_codename != 'All', sprintf('%.1f', .), format(round(., 0), big.mark = ','))),
            across(no_col:not_first, ~ if_else(table == 'count_table' | (table == 'col_pct_table' & eps_codename == 'All'), format(round(., 0), big.mark = ','), sprintf('%.1f', .)))
          ) %>%
          select(-unknown, -table, -order_ids, -test_range),
        align = 'lrrrrr', escape = F,
        col.names = c('', 'All', 'First-gen known', 'No college', 'Some college', 'Not first-gen')
      ) %>% 
        pack_rows(index = orders_group, colnum = 1, label_row_css = 'background-color: #eaeaea; padding: 10px 7.5px;') %>% 
        pack_rows(index = rep(tables_group, length(orders)), colnum = 1, label_row_css = '')
    )
  } else if (table_type == 'race_firstgen') {
    group_df <- table_df %>% group_by(order_ids, stu_race_cb) %>% summarise(n = n())
    race_group <- group_df$n
    names(race_group) <- str_replace(str_to_title(group_df$stu_race_cb), 'Or', 'or')

>>>>

    return(
      kbl(
        table_df %>%
          mutate(
            across(all, \(x) format(round(x, 0), big.mark = ',')),
            across(known, ~ if_else(table == 'col_pct_table' & eps_codename != 'All', sprintf('%.1f', .), format(round(., 0), big.mark = ','))),
            across(no_col:not_first, ~ if_else(table == 'count_table' | (table == 'col_pct_table' & eps_codename == 'All'), format(round(., 0), big.mark = ','), sprintf('%.1f', .)))
          ) %>%
          select(-unknown, -table, -order_ids, -test_range),
        align = 'lrrrrr', escape = F,
        col.names = c('', 'All', 'First-gen known', 'No college', 'Some college', 'Not first-gen')
      ) %>% 
        pack_rows(index = orders_group, colnum = 1, label_row_css = 'background-color: #eaeaea; padding: 10px 7.5px;') %>% 
        pack_rows(index = rep(tables_group, length(orders)), colnum = 1, label_row_css = '')
    )
  } else if (table_type == 'race_firstgen') {
    x <- unique(table_df$eps_codename)  # Move "All" row to the end after rest of EPS rows
    table_df$eps_codename <- factor(table_df$eps_codename, levels = c(x[x != 'All'], 'All'))
    table_df <- table_df %>% arrange(order_ids, stu_race_cb, eps_codename)

    group_df <- table_df %>% group_by(order_ids, stu_race_cb) %>% summarise(n = n())
    race_group <- group_df$n
    names(race_group) <- str_replace(str_to_title(group_df$stu_race_cb), 'Or', 'or')
